\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-18 doc/paper.Rmd
images

More precisely, let us define starting points $s_i^{(k)}$ for each signature $k = 1, 2$ as 
\begin{eqnarray*}
s^{(k)}_i = 
\begin{cases}
t_k^* + i w_v & \text{ for } i < 0 \\
t_k^* + w_ o + i w_v & \text{ for } i \ge 0,
\end{cases}
\end{eqnarray*} for integer values of $i$ with $0 <  s^{(k)}_i \le T_k - w_v$.

@@

@@

Looking closer, we see that the problem lies in the way the different-shift pairs are picked: the number of possible different-shift pairs depends on the location of  the  optimal locations $t_1^o$ and $t_2^o$. Whenever are close to the boundaries, the number of possible pairings decreases and reaches zero, if $t_i^{(o)} < w_v$ or  $t_i^{(o)} > T_i-w_o- w_v$. For uniformly distributed locations $t_i^{(o)}$, this results in an expected rate of failure of $2 w_v / (T_i-w_o)$, or about 5.6\% for an average length of $T_i$ of 1200 pixels, $w_o = 120$ pixels and $w_v = 30$ pixels.

>>>>

More precisely, let us define starting points $s_i^{(k)}$ for each signature $k = 1, 2$ as 
\begin{eqnarray}\label{eq.start}
s^{(k)}_i = 
\begin{cases}
t_k^* + i w_v & \text{ for } i < 0 \\
t_k^* + w_ o + i w_v & \text{ for } i \ge 0,
\end{cases}
\end{eqnarray} for integer values of $i$ with $0 <  s^{(k)}_i \le T_k - w_v$.

@@

## A problem with failures and modification

Looking closer at \autoref{eq.start}, we see that by definition, some number of tests will fail to produce a result, either because the number of eligible same-shift pairs is zero, or the number of different-shift opairs is zero.

The number of same-shift pairs will be zero, if the optimal locations $t_1^{o}$ and $t_2^{o}$ are so far apart, that no segments of size $w_v$ are left on the same sides of the optimal locations, i.e. $t_1^{o} < w_v$ and $t_2^{o} > T_2-w_o-w_v$ or  $t_1^{o} < T_1- w_o - w_v$ and $t_2^{o} < w_v$. For uniformly distributed optimal locations, we expect to see these situation with a probability of $\frac{2 w_v^2}{(T_1-w_o)(T_2-w_o)}$. For  an average length of $T_i$ of 1200 pixels, $w_o = 120$ pixels and $w_v = 30$ pixels this probability is about 0.0015.

The number of possible different-shift pairs also depends on the location of  the  optimal locations $t_1^o$ and $t_2^o$. Whenever the optimal locations are close to the boundaries, the number of possible pairings decreases and reaches zero, if $t_i^{(o)} < w_v$ or  $t_i^{(o)} > T_i-w_o- w_v$. For uniformly distributed locations $t_i^{(o)}$, this results in an expected rate of failure of $2 w_v / (T_i-w_o)$, or about 5.6\% for an average length of $T_i$ of 1200 pixels, $w_o = 120$ pixels and $w_v = 30$ pixels.

@@

### 2018-04-18 doc/paper.tex
images

\begin{eqnarray*}
s^{(k)}_i = 
\begin{cases}
t_k^* + i w_v & \text{ for } i < 0 \\
t_k^* + w_ o + i w_v & \text{ for } i \ge 0,
\end{cases}
\end{eqnarray*}

@@

@@

Looking closer, we see that the problem lies in the way the
different-shift pairs are picked: the number of possible different-shift
pairs depends on the location of the optimal locations \(t_1^o\) and
\(t_2^o\). Whenever are close to the boundaries, the number of possible
pairings decreases and reaches zero, if \(t_i^{(o)} < w_v\) or
\(t_i^{(o)} > T_i-w_o- w_v\). For uniformly distributed locations
\(t_i^{(o)}\), this results in a probability of failure of
\(2 w_v / (T_i-w_o)\), or about 5.6\% for an average length of \(T_i\)
of 1200 pixels, \(w_o = 120\) pixels and \(w_v = 30\) pixels.

>>>>

\begin{eqnarray}\label{eq.start}
s^{(k)}_i = 
\begin{cases}
t_k^* + i w_v & \text{ for } i < 0 \\
t_k^* + w_ o + i w_v & \text{ for } i \ge 0,
\end{cases}
\end{eqnarray}

@@

\subsection{A problem with failures and
modification}\label{a-problem-with-failures-and-modification}

Looking closer at \autoref{eq.start}, we see that by definition, some
number of tests will fail to produce a result, either because the number
of eligible same-shift pairs is zero, or the number of different-shift
opairs is zero. The number of same-shift pairs will be zero, if the
optimal locations \(t_1^{o}\) and \(t_2^{o}\) are so far apart, that no
segments of size \(w_v\) are left on the same sides of the optimal
locations, i.e. \(t_1^{o} < w_v\) and \(t_2^{o} > T_2-w_o-w_v\) or
\(t_1^{o} < T_1- w_o - w_v\) and \(t_2^{o} < w_v\). For uniformly
distributed optimal locations, we expect to see these situation in
\(2 \times \frac{w_v^2}{(T_1-w_o)(T_2-w_o)}\)

problem lies in the way the different-shift pairs are picked: the number
of possible different-shift pairs depends on the location of the optimal
locations \(t_1^o\) and \(t_2^o\). Whenever are close to the boundaries,
the number of possible pairings decreases and reaches zero, if
\(t_i^{(o)} < w_v\) or \(t_i^{(o)} > T_i-w_o- w_v\). For uniformly
distributed locations \(t_i^{(o)}\), this results in an expected rate of
failure of \(2 w_v / (T_i-w_o)\), or about 5.6\% for an average length
of \(T_i\) of 1200 pixels, \(w_o = 120\) pixels and \(w_v = 30\) pixels.

@@
